|

### 2025-01-24 doc/paper.qmd
sync latest
another one

## Results {#sec-results1}
To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`. The analysis of market shares for statutory audits across European countries reveals distinct patterns of market concentration and auditor dominance. Big 4 firms exhibit a significant presence, often commanding a dominant share in many countries. For example, countries such as the Czech Republic, Estonia, and Finland demonstrate Big 4 market shares exceeding 95%, reflecting the significant influence of these firms in specific markets. However, the extent of this dominance varies, with lower Big 4 shares observed in countries like Bulgaria (17.5%) and Greece (43.6%), indicating a more diversified audit market in these regions. The analysis reveals that the Big 4 hold a market share exceeding 80% in 11 EU countries. This aligns with rthe finding of @EC_Report_2024, which similarly highlights that the Big 4 dominate over 80% of the market share in 11 Member States.

>>>>

## Results {#sec-results1}
Comparing our replication results of Figure 1 (see Figure ## below) with those in the original report (see Figure 1 below) reveals both similarities and discrepancies.

```{python}
#| label: fig1_original_png
#| fig-cap: "Original Figure 1 from Ball and Shivakumar (2008)"
#| echo: false

from IPython.display import Image

Image(filename="fig1_original.png")
```

To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`. The analysis of market shares for statutory audits across European countries reveals distinct patterns of market concentration and auditor dominance. Big 4 firms exhibit a significant presence, often commanding a dominant share in many countries. For example, countries such as the Czech Republic, Estonia, and Finland demonstrate Big 4 market shares exceeding 95%, reflecting the significant influence of these firms in specific markets. However, the extent of this dominance varies, with lower Big 4 shares observed in countries like Bulgaria (17.5%) and Greece (43.6%), indicating a more diversified audit market in these regions. The analysis reveals that the Big 4 hold a market share exceeding 80% in 11 EU countries. This aligns with rthe finding of @EC_Report_2024, which similarly highlights that the Big 4 dominate over 80% of the market share in 11 Member States.
